\section{General Meetings}
\subsection{Annual General Meetings—holding of}
\begin{enumerate}
  \item With the exception of the first Annual General Meeting of the Association, the Association must, at least once in each calendar year and within the period of 6 months after the expiration of each financial year of the Association, convene an Annual General Meeting of its members.
  \item The Association must hold its first Annual General Meeting:
    \begin{enumerate}
      \item within the period of 18 months after its incorporation under the Act, and
      \item within the period of 6 months after the expiration of the first financial year of the Association.
    \end{enumerate}
  \item Clauses (1) and (2) have effect subject to any extension or permission granted by the Director-General under section 26 (3) of the Act.
\end{enumerate}
\subsection{Annual General Meetings—calling of and business at}
\begin{enumerate}
  \item The Annual General Meeting of the Association is, subject to the Act and to rule 23, to be convened on such date and at such place and time as the committee thinks fit.
  \item In addition to any other business which may be transacted at an Annual General Meeting, the business of an Annual General Meeting is to include the following:
    \begin{enumerate}
      \item to confirm the minutes of the last preceding Annual General Meeting and of any Special General Meeting held since that meeting,
      \item to receive from the committee reports on the activities of the Association during the last preceding financial year,
      \item to elect office-bearers of the Association and ordinary members of the committee,
      \item to elect the Public Officer of the Association, and
      \item to receive and consider the statement which is required to be submitted to members under section 26 (6) of the Act.
    \end{enumerate}
  \item An Annual General Meeting must be specified as such in the notice convening it.
\end{enumerate}
\subsection{Special General Meetings—calling of}
\begin{enumerate}
  \item The committee may, whenever it thinks fit, convene a Special General Meeting of the Association.
  \item The committee must, on the requisition in writing of not less than 12 financial members, convene a Special General Meeting of the Association.
  \item A requisition of members for a Special General Meeting:
    \begin{enumerate}
      \item must state the purpose or purposes of the meeting, and
      \item must be signed by the members making the requisition, and
      \item must be lodged with the secretary, and
      \item may consist of several documents in a similar form, each signed by one or more of the members making the requisition.
    \end{enumerate}
  \item If the committee fails to convene a Special General Meeting to be held within 1 month after that date on which a requisition of members for the meeting is lodged with the secretary, any one or more of the members who made the requisition may convene a Special General Meeting to be held not later than 3 months after that date.
  \item A Special General Meeting convened by a member or members as referred to in clause (4) must be convened as nearly as is practicable in the same manner as General Meetings are convened by the committee and any member who consequently incurs expense is entitled to be reimbursed by the Association for any expense so incurred.
\end{enumerate}
\subsection{Notice}
\begin{enumerate}
  \item Except if the nature of the business proposed to be dealt with at a General Meeting requires a special resolution of the Association, the secretary must, at least 14 days before the date fixed for the holding of the General Meeting, give a notice to each member specifying the place, date and time of the meeting and the nature of the business proposed to be transacted at the meeting.
  \item If the nature of the business proposed to be dealt with at a General Meeting requires a special resolution of the Association, the secretary must, at least 21 days before the date fixed for the holding of the General Meeting, cause notice to be given to each member specifying, in addition to the matter required under clause (1), the intention to propose the resolution as a special resolution.
  \item No business other than that specified in the notice convening a General Meeting is to be transacted at the meeting except, in the case of an Annual General Meeting, business which may be transacted under rule 24 (2).
  \item A member desiring to bring any business before a General Meeting may give notice in writing of that business to the secretary who must include that business in the next notice calling a General Meeting given after receipt of the notice from the member.
\end{enumerate}
\subsection{Procedure}
\begin{enumerate}
  \item No item of business is to be transacted at a General Meeting unless a quorum of members entitled under these rules to vote is present during the time the meeting is considering that item.
  \item Eleven members present in person (being members entitled under these rules to vote at a General Meeting) constitute a quorum for the transaction of the business of a General Meeting.
  \item If within half an hour after the appointed time for the commencement of a General Meeting a quorum is not present, the meeting:
    \begin{enumerate}
      \item if convened on the requisition of members, is to be dissolved, and
      \item in any other case, is to stand adjourned to the same day in the following week at the same time and (unless another place is specified at the time of the adjournment by the person presiding at the meeting or communicated by written notice to members given before the day to which the meeting is adjourned) at the same place.
    \end{enumerate}
  \item If at the adjourned meeting a quorum is not present within half an hour after the time appointed for the commencement of the meeting, the members present (being not less than seven) is to constitute a quorum.
\end{enumerate}

\subsection{Presiding member}
\begin{enumerate}
  \item The president or, in the president`s absence, the vice-president, is to preside as chairperson at each General Meeting of the Association.
  \item If the president and the vice-president are absent or unwilling to act, the members present must elect one of their number to preside as chairperson at the meeting.
\end{enumerate}

\subsection{Adjournment}
\begin{enumerate}
  \item\label{adjournment1} The chairperson of a General Meeting at which a quorum is present may, with the consent of the majority of members present at the meeting, adjourn the meeting from time to time and place to place, but no business is to be transacted at an adjourned meeting other than the business left unfinished at the meeting at which the adjournment took place.
  \item\label{adjournment2} If a General Meeting is adjourned for 14 days or more, the secretary must give written or oral notice of the adjourned meeting to each member of the Association stating the place, date and time of the meeting and the nature of the business to be transacted at the meeting.
  \item Except as provided in clauses (\ref{adjournment1}) and (\ref{adjournment2}), notice of an adjournment of a General Meeting or of the business to be transacted at an adjourned meeting is not required to be given.
\end{enumerate}

\subsection{Making of descisions}
\begin{enumerate}
  \item A question arising at a General Meeting of the Association is to be determined on a show of hands and, unless before or on the declaration of the show of hands a poll is demanded, a declaration by the chairperson that a resolution has, on a show of hands, been carried or carried unanimously or carried by a particular majority or lost, or an entry to that effect in the minute book of the Association, is evidence of the fact without proof of the number or proportion of the votes recorded in favour of or against that resolution.
  \item At a General Meeting of the Association, a poll may be demanded by the chairperson or by at least 3 members present in person or by proxy at the meeting.
  \item If a poll is demanded at a General Meeting, the poll must be taken:
  \begin{enumerate}
    \item immediately in the case of a poll which relates to the election of the chairperson of the meeting or to the question of an adjournment, or
    \item in any other case, in such manner and at such time before the close of the meeting as the chairperson directs,
  \end{enumerate}
  and the resolution of the poll on the matter is taken to be the resolution of the meeting on that matter.
\end{enumerate}

\subsection{Special resolution}
A resolution of the Association is a special resolution:
\begin{enumerate}
  \item if it is passed by a majority which comprises at least three-quarters of the members present in person or by proxy at the General Meeting of which not less than 21 days’ written notice specifying the intention to propose the resolution as a special resolution was given in accordance with these rules, or
  \item where it is made to appear to the Director-General that it is not practicable for the resolution to be passed in the manner specified in paragraph (a), if the resolution is passed in a manner specified by the Director-General.
\end{enumerate}

\subsection{Voting}
\begin{enumerate}
  \item On any question arising at a General Meeting of the Association a member has one vote only.
  \item All votes must be given personally or by proxy but no member may hold more than three proxies.
  \item In the case of an equality of votes on a question at a General Meeting, the chairperson of the meeting is entitled to exercise a second or casting vote.
  \item A member or proxy is entitled to vote at the Annual General Meeting providing all fees due and payable (in accordance with Rule 8) have been paid for the financial year to which the financial reports refer.
  \item A member or proxy is entitled to vote at any General Meeting (excluding the Annual General Meeting) providing all fees due and payable (in accordance with Rule 8) have been paid.
\end{enumerate}

\subsection{Appointment of proxies}
\begin{enumerate}
  \item Each member is to be entitled to appoint another member as proxy by notice given to the secretary no later than 24 hours before the time of the meeting in respect of which the proxy is appointed.
  \item The notice appointing the proxy is to be in the form set out in Appendix 2 to these rules.
\end{enumerate}
