\section{Miscellaneous}

\subsection{Insurance}
The Association must effect and maintain insurance.

\subsection{Funds - source}
\begin{enumerate}
  \item The funds of the Association are to be derived from entrance fees and annual subscriptions of members, donations and, subject to any resolution passed by the Association in General Meeting, such other sources as the committee determines.
  \item All money received by the Association must be deposited within 14 days from receipt, and without deduction, to the credit of the Association’s bank account.
  \item The Association must, as soon as practicable after receiving any money, issue an appropriate receipt.
\end{enumerate}

\subsection{Funds - management}
\begin{enumerate}
  \item Subject to any resolution passed by the Association in General Meeting, the funds of the Association are to be used in pursuance of the object of the Association in such manner as the committee determines.
  \item All cheques, drafts, bills of exchange, promissory notes and other negotiable instruments must be signed in accordance with Rule 17 of the Constitution.
\end{enumerate}

\subsection{Alteration of object and rules}
The statement of object and these rules may be altered, rescinded or added to only by a special resolution of the Association.

\subsection{Not-for-profit}
\begin{enumerate}
  \item In furtherance to rule 1.2, the funds of the Association must not be distributed directly to its members.
  \item Rule 5.5 (1) does not stop the Association from paying a member as follows, provided it is done in good faith and the payment is at fair and reasonale rates or rates more favourable to the Association:
    \begin{enumerate}
      \item for goods or services he or she has provided to the Association; or
      \item for expenses that he or she has properly incurred for the benefit of the Association.
    \end{enumerate}
\end{enumerate}

\subsection{Dissolution}
In the event of the Association being dissolved, all assets and funds that remain after such dissolution and the satisfaction of all debts and liabilities must be trandferred to another organisation with similar purposes, which is charitable at law and which has rules prohibiting the distribution of its assets and income to its members.
