\section{Preliminary}

\subsection{Name of Association}
The Association shall be called Manly Musical Society Inc (hereinafter referred to as the Association), also referred to as MMS.
\subsection{Object of the Association}
The object of Manly Musical Society Inc is the presentation of musical theatre.  The Association will achieve this by the cultivation of vocal music by practice and subsequent public performance.  The Association is not carried on for the personal gain of any member or members.  Any profits derived from performances of the Association will be paid into the Association’s funds for furtherance of the aims and object of the Association or for donation to any charity.
\subsection{Registered Address}
The registered address of the Association is the residential address of the Public Officer of the Association.
\subsection{Definitions}
In these rules, the following roles are defined as:
\begin{enumerate}
  \item \textit{Director-General} means the Director-General of the Department of Fair Trading.
  \item \textit{Ordinary member} member means a member of the committee who is not an office-bearer of the Association, as referred to in rule 14 (2).
  \item \textit{Secretary} means:
    \begin{enumerate}
      \item the person holding office under these rules as secretary of the Association, or
      \item if no such person holds that office—the public officer of the Association.
    \end{enumerate}
  \item \textit{Public officer} means:
    \begin{enumerate}
      \item the person appointed by the Association under the rules of the Association.
    \end{enumerate}
\end{enumerate}
In these rules, the following terms are defined as:
\begin{enumerate}
  \item \textit{The Act} means the \underline{\href{https://legislation.nsw.gov.au/\#/view/act/1984/143/full}{Associations Incorporation Act 1984}}.
  \item \textit{The Regulation} means the \underline{\href{https://www.legislation.nsw.gov.au/\#/view/subordleg/1999/484}{Associations Incorporation Regulation 1999}}.
\end{enumerate}
In these rules:
\begin{enumerate}
  \item A reference to a function includes a reference to a power, authority and duty.
  \item A reference to the exercise of a function includes, if the function is a duty, a reference to the performance of the duty.
  \item The provisions of the Interpretation Act 1987 apply to and in respect of these rules in the same manner as those provisions would so apply if these rules were an instrument made under the Act.
\end{enumerate}

